Local PCA results

### 2017-10-08 sims/msp/summarize_run.Rmd
.

Here is the color scheme:
```{r pop_colors, fig.height=2*fig.dim}
pop.names <- levels(samps$population)
pop.cols <- rainbow_hcl(nlevels(samps$population))
pop.pch <- seq_len(nlevels(samps$population))
plot( rep(1,length(pop.names)), seq_along(pop.names), 
       cex=4, pch=pop.pch, col=pop.cols, xlim=c(0,length(pop.names)),
       xlab='', ylab='', xaxt='n', yaxt='n' )
text( rep(1,length(pop.names)), seq_along(pop.names), labels=pop.names, pos=4 )
```

>>>>

Here is the color scheme:
```{r pop_colors, fig.height=2*fig.dim}
pop.names <- levels(samps$population)
dim(pop.names) <- c(10,10)
pop.cols <- rainbow_hcl(nlevels(samps$population))
# max pch value is 25
# pop.pch <- seq_len(nlevels(samps$population)) %% 25
pop.pch <- rep(c(0:4,14:18),10)
plot( row(pop.names), col(pop.names),
       cex=4, pch=pop.pch, col=pop.cols,
       xlab='', ylab='', xaxt='n', yaxt='n' )
text( rep(1,length(pop.names)), seq_along(pop.names), labels=pop.names, pos=4 )
```
